\section*{\color{SectionBlue}{Conclusion}} \label{sec:sections}
\addcontentsline{toc}{section}{Conclusion}

The first part of this research was concentrated on  developing an effective algorithm to optimize the knapsack problem. However, beyond that, this researcher has applied that algorithm to the real-world scenario of cybersecurity investment. From this research, an effective algorithm, Quantum Save, was developed on the IBM Q32 quantum simulator that increases the optimization of the knapsack problem. Due to the success of this algorithm in optimizing the knapsack problem, Quantum Save can be used for multiple practical applications. One application for Quantum Save is towards system design, which is a knapsack problem that can have major impact on the world as a whole. Essentially, system design process translates the customers’ needs into a buildable system design that selects subsystems from an allowable set while remaining under a corporate budget. Chapman et al. \cite{chapman_system_2001} in an analysis of the system design process explain how system design problem is NP-complete similar to the Knapsack problem \cite{chapman_system_2001}. Both of these problems are attempting to maximize a certain value, either the required system performance or the amount of money in the knapsack, while remaining under a certain restraint, including a weight cap and a certain budget. Computer science is an ever-evolving field of study and finding the optimal solution to these fundamental problems, such as the knapsack problem, could be extremely beneficial especially as technology continues to grow. 

\vspace{1mm}

\indent Apart from the actual optimization of the knapsack problem, an accurate model for cyber security investment was proposed. Using Quantum Save, an optimal investment plan will be provided to the CISO so that his or her small-medium enterprise will be protected against the malicious attacks implemented by a hacker. The known vulnerabilities in the system will be handled and the company can perform more research and development without worrying that their database will be compromised. In this online network that society has woven in the modern world, the importance of keeping information safe cannot be emphasized enough. If a company has a bad security system implemented and their data is vulnerable to hackers from all around the world, the government and other business contractors will not want to do business. The reputation of these small-medium enterprises relies on the idea that their backend is secure enough so that the confidential data which will be entrusted to them doesn't get lost. With this cyber security investment plan, small-medium enterprises will have the means of strengthening their backend and increasing their reputation within society. In a modern wold where everyone's personal information is vulnerable, it is important for companies to invest in protecting that information and helping every person in the American society. Quantum Save can help small-medium compenies and hospitals save millions of dolalrs by effectively allocating cybersecurity budgets.
